Etox-Base: A tool to derive exposure endpoints from chemical test results

### 2019-02-05 article/test.tex
Updates from Overleaf

\pgfplotstabletypeset[
    col sep=comma,
    string type,
    columns={script,[index]2},
    ]{data/scripts.csv}

>>>>

\pgfplotstabletypeset[
    col sep=comma,
    string type,
    columns={Script,Description},
    columns/Description/.style={column type={|l}},
    columns/Script/.style={column type={|l}, % needed for replacing underscore
                           postproc cell content/.code={%
                                \pgfplotsutilstrreplace{_}{\_}{##1}%
                                \pgfkeyslet{/pgfplots/table/@cell content}\pgfplotsretval
                                },
                            },
    every head row/.style={before row=\hline,after row=\hline},
	every last row/.style={after row=\hline},
    ]{data/scripts.csv}
